DeepSphere: a graph-based spherical CNN

### 2019-09-24 main.tex
small edits

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.
The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).

@@

Results are shown in \tabref{shrec17}.
DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
% x times faster
As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}

@@

\subsection{Uneven sampling} \label{sec:exp:ghcn}

@@

\newpage
\subsubsection*{Author Contributions}
Left blank for anonymity reason
% If you'd like to, you may include a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Left blank for anonymity reason

@@

* Network architecture and details

>>>>

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).

@@

Results are shown in \tabref{shrec17}.
DeepSphere achieves the same performance as \citet{cohen2018sphericalcnn} and \citet{esteves2018sphericalcnn} at a much lower cost, suggesting that anisotropic filters are an unnecessary price to pay.
% x times faster
As the information in those spherical maps resides in the low frequencies (\figref{spectrum}), reducing the equivariance error didn't translate into improved performance.
For the same reason, using the more uniform HEALPix discretization or lowering the resolution down to $N_{side} = 8$ didn't impact performance.
\todo{be sure that it fits with the cosmo conclusion}
\todo{The same conclusions are drawn from ModelNet 40 (see appendix ??).}

@@

\subsection{Uneven sampling} \label{sec:exp:ghcn}
% Weather prediction? But it's not a real task. Rather a demo.

@@

\newpage
\subsubsection*{Author Contributions}
Left blank for anonymity reason.
% If you'd like to, you may include a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Left blank for anonymity reason.

@@

* Network architecture and training details
